---
title: "Lab 03 - Nobel laureates"
author: "Natalie Frye"
date: "2/10/2021"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r data-overview}
glimpse(nobel)
```

There are 26 variables and 935 observations in this dataset. Each row represents a nobel laureate. 

### Exercise 2

```{r nobel-living-dataframe}
nobel_living <- nobel %>%
  filter(
    !is.na(country),
    gender != "org",
    is.na(died_date)
    )
glimpse(nobel_living)
```

### Defining Dataframe

```{r mutate-country_us}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  ) 
```

```{r filter-by-science}
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```
### Exercise 3
```{r plot-country-by-category}
ggplot(data = nobel_living_science, 
      mapping = aes(x = country_us,
                    color = country_us, fill = country_us)) +
    geom_bar() +
    coord_flip() +
    facet_wrap(~ category) +
  labs(title = "US vs. non-US Laureates by Category", 
       x = "Living in US or other",
       y = "Number of laureates") 
  
```

It appears to be true that more nobel laureates were living in the US when they received their prize than were living in other countries. This imbalance is most true in the category of economics, and least true in the category of chemistry.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
